Particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2025-11-16 AvdMomZvolA_examples/ips_examples.tex
[AMZA] Remove duplicate citation

For convenience, we use the notation \cite{our-ped-2018,our-pmm-2018,our-vmmsh-2018}:
$\sqrt{p}/q * \{ (x_1,y_1), ...,$ $ (x_n, y_n)  \}$,
which means that each abscissa is multiplied by $1/q$
and each ordinate is multiplied by $\sqrt{p}/q$,  i.e.
\begin{equation}
	\label{eq:char_lattice}
	\sqrt{p}/q * \{ (x_1,y_1), ..., (x_n, y_n)  \}
	=
	\left\{ \left(\frac{x_1}{q},\frac{y_1\sqrt{p}}{q}\right), ..., \left(\frac{x_n}{q},   \frac{y_n\sqrt{p}}{q}\right)  \right\}
	.
\end{equation}
Here $q$ is the characteristic of the PIPS;
every PIPS can be represented in such way~\cite[Theorem 4]{our-vmmsh-2018-translit}.

>>>>

For convenience, we use the notation \cite{our-ped-2018,our-pmm-2018,our-vmmsh-2018-translit}:
$\sqrt{p}/q * \{ (x_1,y_1), ...,$ $ (x_n, y_n)  \}$,
which means that each abscissa is multiplied by $1/q$
and each ordinate is multiplied by $\sqrt{p}/q$,  i.e.
\begin{equation}
	\label{eq:char_lattice}
	\sqrt{p}/q * \{ (x_1,y_1), ..., (x_n, y_n)  \}
	=
	\left\{ \left(\frac{x_1}{q},\frac{y_1\sqrt{p}}{q}\right), ..., \left(\frac{x_n}{q},   \frac{y_n\sqrt{p}}{q}\right)  \right\}
	.
\end{equation}
Here $q$ is the characteristic of the PIPS;
every PIPS can be represented in such way~\cite[Theorem 4]{our-vmmsh-2018-translit}.
